We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-03 paper/paper.tex
some pagragraphs

Studies of the Local Group in an explicit cosmological context have
also renewed the interest on performing constrained simulations that
could reproduce the observed large scale structure of the Universe,
This has also motivated the study of the two dominant galaxies in the 
Local Group as a pair in a cosmological context.

@@

\label{Data Samples}

>>>>

Studies of the Local Group in an explicit cosmological context have
also renewed the interest on performing constrained simulations that
could reproduce the observed large scale structure of the Universe,
This has also motivated the study of the two dominant galaxies in the 
Local Group as a pair in a cosmological context finding that the LG
itself has relatively uncommon kinematic configuration in the context
of LCDM and a strong preference to lie along filaments.

The aim of our work is to put together some of these pieces in a 
simple framework to quantify how atypical is the satellite
distribution found in the Local Group.
Some of the explicit characteristics we want to keep in our treatment
of the problem are the (i) cosmological context, (ii) the LG as a pair
of galaxies and (iii) a simple and robust description for the
satellites.

The first condition constrains the kind of simulations we use. 
We either results from fully cosmological simulations or resimulations
of cosmological sub-volumes. 
The second condition constraints the kind of samples we want to
use. We build explicit samples of pairs that resemble the kinematic
structure of the MW and M31. 
The third condition motivates to only use the inertia tensor as a
description for the satellites positions, while droping any
information that might come from 3D velocities (high uncertainties) or
involved algorithms for plane fitting.

Finally,

@@

\section{Data samples}
